\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-27 paper.tex
Proof read part 2

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{overview}
    \caption{Schema of a possible \uwds network: eight possible, user-written
    \emph{clients} (in blue) are sharing environment models through four
    independent \emph{worlds} (made of joint spatial and temporal models). This architecture
    enables successive and modular refinement of the models
    (\emph{cascading} situation assessment), effectively adapted to each
    client's needs (yellow nodes represent other possible components in the system that do not
    interact directly with the \uwds network).}

@@

\uwds addresses this need and the main contribution of this work is a generic
approach to \textbf{represent and share multiple parallel representations of the
world}. \uwds does so by permitting clients to clone existing worlds, modify
them, and re-share them, without the cost of duplicating geometric data (as
explained in section~\ref{design}). By organizing clients in a network
(Figure~\ref{fig|scene}), worlds can be made dependent on each other, resulting
in a loosely-coupled modular approach to spatio-temporal world representation
that we call \emph{cascading situation assessment}.

@@

Figure~\ref{fig|scene} pictures a typically \uwds topology: a graph (that
happens to be a directed acyclic graph on Figure~\ref{fig|scene}, but does not
have to be in the general case -- cycles are permitted) of \emph{clients}
connected through shared data structures called \emph{worlds}.

@@

Software components accessing \uwds worlds are called clients. Some standard
clients (like a 3D visualization tool) are provided with the \uwds package (see
section~\ref{std_clients}), but clients are otherwise written by the end users
using the \uwds client API (see section~\ref{api}).

Clients can both read and write onto the worlds they are connected to, and
automatically see updates broadcasted by other clients connected to the same
worlds.

@@

Each world is technically independent from every others. Dependencies between
worlds arise from the clients' connections. For instance, filters effectively
create a dependency between worlds. A client like the \textit{Physics-based
position correction} client create a dependency between the world {\tt base} (which
represents here the result of raw sensor fusion) and the world {\tt corrected}
which would be a physically-consistent copy of {\tt base}.
As a result, an \uwds network can be seen as a dependency graph between worlds (where
cyclic dependencies are permissible).

@@

\emph{Worlds} contain both a geometric model and a temporal model. The geometric
model is represented as a scene graph. The scene graph has a unique root node,
to which a tree of other nodes is parented.

Nodes in the scene graph have four possible types: \textbf{objects} that represent
concrete physical objects (typically with one or several associated 3D meshes);
\textbf{entities} that represent abstract entities like reference frames or
groups of objects; \textbf{perspectives} that represent viewpoints onto the
scene (like cameras or human gaze); and \textbf{fields} that represent scalar or
vector fields (like the visibility of an object, the working space of robot,
etc. -- note that fields are not yet implemented in the current version of
\uwds, see section~\ref{futurework}).

Every node has a unique ID, a parent, a 3D transformation relative to the parent
and an optional name. \emph{Object} nodes optionally store as well pointers to their
associated meshes. Importantly, mesh data (or other geometric datasets like
point clouds) are \emph{not} stored within the nodes. \uwds represents geometric
data as immutable data, labelled with their hash (preventing data duplication).
Nodes only store the hash of their geometric data, and the actual data is pulled
by client whenever they actually need it (for rendering for instance).

@@

Complementing the spatial representation encapsulated in the scene graph, each
world also store the world's \emph{timeline}. This data structure is shared
and synchronized amongst the clients in the same way as the scene graph.
Client can record in the timeline both \emph{events} (duration-less state) and
\emph{situations}, \ie states with a start time and a (possibly open-ended) end time.

@@

\uwds is not a monolithic piece of software. Instead, it stands for both a
\emph{network of interconnected clients} which manipulate spatial and temporal
models of the robot environment (for instance, a motion planner, a object
detection module, a human skeleton tracker, etc.), and for a {client library}
that makes it easy to interface existing software components with the network.

Critically, the network is essentially hidden to the client: from the user
perspective, the environment model is manipulated as local data structures (the
\emph{worlds}). Modifications to the model are asynchronously synchronised with
a central server (the {\tt underworlded} daemon) and broadcasted to every other
client in the network.

As previously mentioned, worlds are composite data structures comprising of a
scene graph and a timeline. These data structures are synchronized using
Google's gRPC message passing framework\footnote{\url{http://www.grpc.io/}}, ensuring
high throughput, reliability, cross-platform/cross-language support. The \uwds
API is specifically discussed hereafter, section~\ref{api}.

\subsubsection*{Performance considerations}

\uwds is meant to broadcast complex environment representations (typically
including large geometric datasets, like meshes) in real-time. \uwds itself does
not perform many CPU intensive tasks (CPU intensive processing tasks -- sensor fusion, physics
simulation, etc. -- are realized by the clients) and as such, the performance
bottleneck is essentially the network's data throughput.

In that regard, one of the simple yet critical optimization performed by \uwds
is automatic caching of mesh data. Mesh data are not transmitted when nodes are
updated; only a hash value of the mesh data. The client can then request the
full data whenever they actually need it.

@@

As mentioned in section~\ref{arch}, \uwds uses Google's gRPC as message passing
protocol. The protocol is explicitly defined (using the \emph{protocol
buffers}\footnote{\url{https://developers.google.com/protocol-buffers/}}
interface definition language), and bindings to various languages
and platforms can be automatically generated from the protocol definition file
(as of Feb 2017, gRPC can generate bindings for C, C++, C\#, Node.js, PHP, Ruby,
Python, Go and Java on Windows, Mac and Linux).

>>>>

\begin{figure}[ht!]
    \centering
    \includegraphics[width=\linewidth]{overview}
    \caption{Schema of a possible \uwds network: eight (user-written \&
    architecture specific) \emph{clients} (in blue) are sharing environment
    models through four independent \emph{worlds} (made of joint spatial and
    temporal models). This architecture enables successive and modular
    refinement of the models (\emph{cascading} situation assessment),
    effectively adapted to each client's needs. \textit{Dashed yellow nodes represent
    other possible components in the system that do not interact directly with
    the \uwds network}.}

@@

\uwds addresses this need and the main contribution of this work is a generic
approach to \textbf{represent and share multiple parallel representations of the
world}. \uwds does so by permitting clients to clone existing worlds, modify
them, and re-share them, without the cost of duplicating geometric data (as
explained at section~\ref{design}). By organizing clients in a network
(Figure~\ref{fig|scene}), worlds can be made dependent on each other, resulting
in a loosely-coupled modular approach to spatio-temporal world representation
that we call \emph{cascading situation assessment}.

@@

Figure~\ref{fig|scene} pictures a typical \uwds topology: a graph (that
happens to be a directed acyclic graph on Figure~\ref{fig|scene}, but does not
have to be in the general case -- cycles are permitted) of \emph{clients}
connected through shared data structures called \emph{worlds}.

@@

Software components accessing \uwds worlds are called clients. Some standard
clients (like a 3D visualization tool) are provided with the \uwds package (see
section~\ref{std_clients}). Clients are otherwise written by the end users
using the \uwds client API (see section~\ref{api}).

Clients can both read and write onto the worlds they are connected to, and
automatically see updates broadcasted by other clients connected to the same
world.

@@

Each world is technically independent from every others. Dependencies between
worlds arise from the clients' connections. For instance, filters effectively
create a dependency between worlds. On Figure~\ref{fig|scene}, the \textit{Physics-based
position correction} client creates a dependency between the world {\tt base} (which
represents here the result of raw sensor fusion) and the world {\tt corrected}
which would be a physically-consistent copy of {\tt base}.
As a result, an \uwds network can be seen as a dependency graph between worlds (where
cyclic dependencies are permissible).

@@

Worlds contain both a geometric model and a temporal model. The geometric
model is represented as a scene graph. The scene graph has a unique root node,
to which a tree of other nodes is parented.

Nodes in an \uwds scene graph have four possible types: \textbf{objects} that
represent concrete physical objects (typically with one or several associated 3D
meshes); \textbf{entities} that represent abstract entities like reference
frames or groups of objects; \textbf{perspectives} that represent viewpoints
onto the scene (like cameras or human gaze); and \textbf{fields} that represent
scalar or vector fields (like the visibility of an object, the working space of
robot, etc. -- note that fields are not yet implemented in the current version
of \uwds, see section~\ref{futurework}).

Every node has a unique ID, a parent, a 3D transformation relative to the parent
and an optional name. \emph{Object} nodes optionally store as well pointers to
their associated meshes. Importantly, mesh data (or other geometric datasets
like point clouds) are \emph{not} stored within the nodes themselves. \uwds
represents geometric data as immutable data, labelled with their hash
(preventing \textit{de facto} data duplication).  Nodes only store the hash
corresponding to the desired geometric data, and the actual data is pulled from
the server by the clients whenever they actually need it (for rendering for
instance).

@@

Complementing the spatial representation encapsulated in the scene graph, each
world also store the world's \emph{timeline}. This data structure is shared
and synchronized amongst the clients in the same way as the scene graph.
Clients can record in the timeline both \emph{events} (duration-less states) and
\emph{situations}, \ie states with a start time and a (possibly open-ended) end time.

@@

\uwds is not a monolithic piece of software. Instead, it stands for both a
\emph{network of interconnected clients} which manipulate spatial and temporal
models of the robot environment (for instance, a motion planner, a object
detection module, a human skeleton tracker, etc.), and for a {client library}
that makes it possible to interface existing software components with the network.

Critically, the network is essentially hidden to the client: from the user
perspective, the environment model is manipulated as a local data structure (see
Listing~\ref{lst|pythonapi}). Modifications to the model are asynchronously synchronised with
a central server (the {\tt underworlded} daemon) and broadcasted to every other
client connected to the same world.

As previously mentioned, worlds are composite data structures comprising of a
scene graph and a timeline. These data structures are synchronized using
Google's gRPC message passing framework\footnote{\url{http://www.grpc.io/}}, ensuring
high throughput, reliability and cross-platform/cross-language support. The \uwds
API is specifically discussed hereafter, at section~\ref{api}.

\uwds is meant to broadcast complex environment representations (typically
including large geometric datasets, like meshes) in real-time. \uwds itself does
not perform many CPU intensive tasks (CPU intensive processing tasks -- sensor
fusion, physics simulation, etc. -- are performed by the clients themselves) and
as such, the performance bottleneck is essentially the network's data
throughput.  In that regard, one of the simple yet critical optimization
performed by \uwds is automatic caching of mesh data. Mesh data are not
transmitted when nodes are updated; only a hash value of the mesh data. The
client can then request the full data whenever they actually need it.

@@

As mentioned at section~\ref{arch}, \uwds uses Google's gRPC as message passing
protocol. The protocol is explicitly defined (using the \emph{protocol
buffers}\footnote{\url{https://developers.google.com/protocol-buffers/}}
interface definition language), and bindings to various languages
and platforms can be automatically generated from the protocol definition file
(as of Feb 2017, gRPC can generate bindings for C, C++, C\#, Node.js, PHP, Ruby,
Python, Go and Java on Windows, Mac and Linux).
